---
title: "QMM_Assignment"
author: "Rohit Raj Naik Banoth"
date: "2024-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Weigelt Corporation has three branch plants with excess production capacity. Fortunately,
the corporation has a new product ready to begin production, and all three plants have this
capability, so some of the excess capacity can be used in this way. This product can be made in
three sizes--large, medium, and small--that yield a net unit profit of $420, $360, and $300,
respectively. Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per
day of this product, respectively, regardless of the size or combination of sizes involved.
The amount of available in-process storage space also imposes a limitation on the production
rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet,
respectively, of in-process storage space available for a day's production of this product. Each
unit of the large, medium, and small sizes produced per day requires 20, 15, and 12 square feet,
respectively.
Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and
small sizes, respectively, would be sold per day.
At each plant, some employees will need to be laid off unless most of the plant’s excess
production capacity can be used to produce the new product. To avoid layoffs if possible,
management has decided that the plants should use the same percentage of their excess capacity
to produce the new product.
Management wishes to know how much of each of the sizes should be produced by each of the
plants to maximize profit.
Solve the problem using lpsolve, or any other equivalent library in R.


#Solution:

```{r}
library(lpSolve)
```


```{r}
table.1 = matrix(c(20,900,420,15,1200,360,12,750,300), nrow = 3, ncol = 3, byrow = TRUE)
 colnames(table.1)<-(c('Required SPace', 'SAles FOrecast-PerDay', 'PRofit'))
 rownames(table.1)<-(c('Large','Medium','Small'))
 print(table.1)
```

```{r}
 table.2=matrix(c(750,900,450), nrow = 3, ncol = 1, byrow = TRUE)
 colnames(table.2)<-(c('Excessive Units Capacity pre Day'))
 rownames(table.2)<-(c('PLant1', 'PLant2','PLant3'))
 table.2
```
Let us now contemplate the objective function. Solve the matrix for the columns in the preceding table. There are twelve constraints and nine decision variables.
```{r}
 OBjective_Function <- c(420,360,300,420,360,300,420,360,300)
 print(OBjective_Function)
```
Evaluate the constraint matrix.
```{r}
#Constraint matrix - LHS
 Lhs_Constraint.matrix <- matrix(c(1,1,1,0,0,0,0,0,0,  #Excessive capacity constraint - Plant1
 0,0,0,1,1,1,0,0,0,  
0,0,0,0,0,0,1,1,1,  
20,15,12,0,0,0,0,0,0, #Storage capacity constraints-Plant1
 0,0,0,20,15,12,0,0,0,
 0,0,0,0,0,0,20,15,12,
 1,0,0,1,0,0,1,0,0,    
#Large Size Sales Forecast
 0,1,0,0,1,0,0,1,0,    
0,0,1,0,0,1,0,0,1,    
#Medium Size Sales Forecast
 #Small Size Sales Forecast 
 6,6,6,-5,-5,-5,0,0,0, # in case same percentage of Excessive capacity is used 
0,0,0,1,1,1,-2,-2,-2,
 3,3,3,0,0,0,-5,-5,-5),nrow = 12,byrow = TRUE )
 print(Lhs_Constraint.matrix)
```

Set the inequality signs now.
```{r}
 DIrections <- c("<=",
 "<=",
 "<=",
 "<=",
 "<=",
 "<=",
 "<=",
 "<=",
 "<=",
 "=",
 "=",
 "="
 )
 print(DIrections)
```
Take into consideration an additional set of Constraint
```{r}
 # Constraint matrix - RHS
 Rhs_Constraint.matrix <- c(750,900,450,
 13000,12000,5000,
 900,1200,750,
 0,0,0
 )
 print(Rhs_Constraint.matrix)
```
Proceed to solve the linear program Proble.
```{r}
 # Setting the problem to Maximization
 Linear_Program.Result <- lp("max", OBjective_Function, Lhs_Constraint.matrix,DIrections, Rhs_Constraint.matrix)
 # Printing the Results
print(Linear_Program.Result)
```
Determine the Decision variables' values now.
```{r}
print(Linear_Program.Result$solution)
```


